Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-09-17 latex/robdml.tex
u

\usepackage{microtype}
\usepackage{xcolor}
\newcommand{\oo}[1]{\textcolor{orange}{#1}}

@@

\author{Mo Zhou ~~~~~~~ Vishal M. Patel\\
Johns Hopkins University\\
{\tt\small mzhou32@jhu.edu ~~ vpatel36@jhu.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}
\maketitle

@@

>>>>

\usepackage{microtype}
\usepackage{xcolor}
\newcommand{\oo}[1]{\textcolor{orange}{#1}}
\include{math_commands.tex}

@@

\author{Mo Zhou ~~~~~~~ Vishal Patel\\
Johns Hopkins University\\
{\tt\small mzhou32@jhu.edu ~~ vpatel36@jhu.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}
\maketitle

@@

% what is deep metric learning

Given a set of data points, a metric gives a distance value between each pair
of them, while Deep Metric Learning (DML) aims to learn such a metric
leveraging the representational power of deep neural networks.
%
DML has been extensively studied~[], and has a wide range of applications
such as image retrieval~[] and face recognition~[].

% why defense in deep metric learning

Despite the improvements of this field thanks to the advancement of deep neural
networks, recent research works suggest that DML models are vulnerable to
adversarial attacks, where an imperceptible perturbation could incur unexpected
or covertly manipulated results~[].
%
Such vulnerability poses safety, security, and fairness concerns in the
applications of DML.
%
For example, impersonation or recognition evation are possible for DML-based
face-identification system~[].
%
Thus, defending a DML model against adversarial attacks and improving its
adversarial robustness could be an important problem.

% existing methods & problem
existing methods and problem.

% for problem 1
solution to problem 1

% for problem 2
solution to problem 2

% evaluation and conclusion
experimetal evaluations

% contributions
In brief, our contribusions include:
